\\fontsize{12pt}{3pt}\\selectfont \\textbf{\\textit{Journal: Ecosphere. Manuscript ID: ECS23-0342. Manuscript type: Article}}

### 2024-02-15 manuscript/manuscriptRW.Rmd
add the reference to the published code

**OPEN RESEARCH STATEMENT:** This paper uses novel protocol, data and
code, alle are available open access. The protocol and the protocol data
is available at @díaz-yáñez2022. The data is available at
@diaz-yanez2023. The repository containing the code used in the
analysis, figure creation and manuscript writing can be downloaded from
XXXXXXX.

>>>>

**OPEN RESEARCH STATEMENT:** This paper uses a novel protocol, data and
code, all are available open access. The protocol and the protocol data
is available at @díaz-yáñez2022. The data is available at
@diaz-yanez2023. The repository containing the code used in the
analysis, figure creation and manuscript writing can be downloaded from
@díaz-yáñez2024.
